Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-07-15 manuscript.tex
updated references
Initial work on random data

As expected, the larger the network, the higher the optimal level. For relatively small datasets (\emph{i.e.} less than 10k cells), the first level of the hierarchy contains a number of groups in line with how many observable populations are. 
%\subsection*{PPBM?}

>>>>

As expected, the larger the network, the higher the optimal level. For relatively small datasets (\emph{i.e.} less than 10k cells), the first level of the hierarchy contains a number of groups in line with how many observable populations are. 
\textcolor{red}{Notwithstanding, cell groups identified at leach level may have a biological interpretation. In particular, groups at deepest levels (0 or 1) may be relevant when studying rare populations. For example, in the hematopoiesis dataset shown in Fig. \ref{Figure_Hemato_Supp}A, groups 11 (DC) and 19 (Lymph) cannot be distinguished from nSBM level 1 and up; a closer investigation to level 0, however, revealed that these cells are clearly separated. To better understand the role of deepest levels, we performed an additional analysis of a single cell dataset of mouse crypt cells \cite{Ayyaz_Kumar_2019}, which was also covered in a recent paper proposing GapClust as an optimal approach to identify rare cell populations \cite{Fa_Wei_Zhou_Johnston_2021}. We sought to identify the four rare populations identified by GapClust. We could identify all but the erythrocyte group (R3) at level 1 of the hierarchy (Fig. FOOBAR), suggesting that studying levels with appropriate community size is a valid method to spot rare populations. Of note, modularity optimisation could not identify Tuft cells in appropriate way (Fig.SUPPFOOBAR), not even at high resolution, hence prompting the development of specific approaches such as GapClust. 
As the size and number of communities is strictly dependent on the \emph{k}NN graph generation, we also investigated how different parameters (\emph{i.e.} number of principal components and number of neighbors) affect the partition structure (Fig SUPPBAZBAZ), again using the Crypt experiment as representative sample. We found, as a general pattern, that increasing the number of neighbors results in more granular structure at level 0, whereas increasing the number of PCs works in opposite direction. Looking at the agreement among different partitions, we found that it is consistent among different solutions, both at level 0 and level 1, with the exception of models for graph derived with low number of PC (Fig. ABRACADABRA)}
%\subsection*{PPBM?}
